On centrality of even orthogonal $\Kt$

### 2016-05-13 paper.tex
Fixed many typos

It is a classical theorem of M.~Kervaire and R.~Steinberg that the stable Steinberg group $\St(R)$ is the universal central extension of $\E(R)$, see \cite[Theorem~III.5.5]{Kbook}.
The unstable analogue of the ``universality'' part of this theorem has been known since 1970's for $\Phi$ with of $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi=\rA_\ell, \rB_\ell, \rC_\ell$), see \cite{St1, KaS}.
However, until recently, the analogue of the ``centrality'' part was only known in the special case $\Phi=\rA_\ell$, $\ell\geq 3$ see~\cite[Corollary~2]{vdK}.
The best known result for other classical $\Phi$ was that the centrality holds ``in the stable range'',
i.\,e. when the dimension of $R$ is suffiently small as compared to the rank of $\Phi$, see~\cite[Corollary~3.4]{St78}.

@@

Now consider the case $j=h$, $i\neq k$
By~\cite[3.12]{vdK} one has $$g\,x(u,\,u_{ij}ac_{ij})g\inv=x(\phi(g)u,\,\phi(g)^*u_{ij}ac_{ij}).$$
Set $u' = \phi(g)u$, since
$\phi(g)^*u_{ij} = t_{kj}(-r) \cdot u_{ij} = e_iu_j - e_ju_i + e_kru_i =u'_{ij}+u'_{ki}r,$ 
we obtain from~\cite[3.11]{vdK} that
$$x(\phi(g)u,\,\phi(g)^* u_{ij} ac_{ij})=x\left(u',\,u'_{ij}c_{ij}a\right)\cdot x\left(u',\,u'_{ki} rc_{ij}a\right).$$
Decomposing in this fashion each factor $g\,x(u,u_{ij}ac_{ij})g^{-1}$ for which $\phi(g)^*u_{ij}ac_{ij}$ does not have two zero coordinates, 
 we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$.

@@

One can repeat van der Kallen's and Tulenbaev's arguments and prove the following transposed version of Lemma~\ref{xproperties}.
We leave the proof of this lemma to the reader.
\begin{lm}
\label{yproperties}
For $u$, $u'$, $w$ and $v\in B^n$, such that $u$ and $u'$ have decomposition as in above definition, $w^tv=0$, $a$, $b\in I(v)$, $c\in B$, $g\in\St(n,\,B)$ holds
\begin{enumerate}
\item $Y_{uc,v}(a)=Y_{u,v}(ca)$,
\item $Y_{u,vc}(ca)=Y_{uc^2,v}(a)$,
\item $Y_{u,v}(a)X_{u',v}(a)=Y_{u+u',v}(a)$,
\item $g\,Y_{wb,v}(a)g\inv=Y_{\phi(g)wb,\phi(g)^*v}(a)$.
\end{enumerate}
\end{lm}

>>>>

It is a classical theorem of M.~Kervaire and R.~Steinberg that the stable Steinberg group $\St(R)$ is the universal central extension of $\E(R)$, see \cite[Theorem~III.5.5]{Kbook}.
The unstable analogue of the ``universality'' part of this theorem has been known since 1970's for $\Phi$ with rank $\ell \geq 5$ (or even $\ell \geq 4$ for $\Phi=\rA_\ell, \rB_\ell, \rC_\ell$), see \cite{St1, KaS}.
However, until recently, the analogue of the ``centrality'' part was only known in the special case $\Phi=\rA_\ell$, $\ell\geq 3$ see~\cite[Corollary~2]{vdK}.
The best known result for other classical $\Phi$ was that the centrality holds ``in the stable range'',
i.\,e. when the dimension of $R$ is suffiently small as compared to the rank of $\Phi$, see~\cite[Corollary~3.4]{St78}.

@@

Now consider the case $j=h$, $i\neq k$.
By~\cite[3.12]{vdK} one has $$g\,x(u,\,u_{ij}ac_{ij})g\inv=x(\phi(g)u,\,\phi(g)^*u_{ij}ac_{ij}).$$
Set $u' = \phi(g)u$, since
$\phi(g)^*u_{ij} = t_{kj}(-r) \cdot u_{ij} = e_iu_j - e_ju_i + e_kru_i =u'_{ij}+u'_{ki}r,$ 
we obtain from~\cite[3.11]{vdK} that
$$x(\phi(g)u,\,\phi(g)^* u_{ij} ac_{ij})=x\left(u',\,u'_{ij}c_{ij}a\right)\cdot x\left(u',\,u'_{ki} rc_{ij}a\right).$$
Decomposing in this fashion each factor $g\,x(u,u_{ij}ac_{ij})g^{-1}$ for which $\phi(g)^*u_{ij}ac_{ij}$ does not have two zero coordinates, 
 we arrive at a product satisfying the requirements of the definition of $X_{\phi(g)u,\phi(g)^*wb}(a)$.

@@

One can repeat van der Kallen's and Tulenbaev's arguments and prove the following transposed version of Lemma~\ref{xproperties}.
We leave the proof of this lemma to the reader.
\begin{lm}
\label{yproperties}
For $u$, $u'$, $w$ and $v\in B^n$, such that $u$ and $u'$ have decomposition as in the above definition, $w^tv=0$, $a$, $b\in I(v)$, $c\in B$, $g\in\St(n,\,B)$ one has
\begin{enumerate}
\item $Y_{uc,v}(a)=Y_{u,v}(ca)$,
\item $Y_{u,vc}(ca)=Y_{uc^2,v}(a)$,
\item $Y_{u,v}(a)X_{u',v}(a)=Y_{u+u',v}(a)$,
\item $g\,Y_{wb,v}(a)g\inv=Y_{\phi(g)wb,\phi(g)^*v}(a)$.
\end{enumerate}
\end{lm}
